데이터 분석가의 R 패키지 개발 도전기

### 2021-10-28 draft.Rmd
마무리 수정

데이터 생성
{{content}}

@@

**함수 1**
{{content}}

@@

**함수 2**
{{content}}

@@

분석
{{content}}

@@

**함수 3**
{{content}}

@@

분석
{{content}}

@@

데이터 생성
{{content}}

@@

**함수 4**
{{content}}

@@

**함수 5**
{{content}}

@@

데이터 분석
{{content}}

@@

````
```{r}`r ''`
library(dmtr)

@@

```{r lda-test, echo = TRUE}
library(testthat); library(dmtr);
test_that("Fisher discriminant function matches", {
  local_edition(3)
  expect_equal(
    fisher_ld(binaryclass2, class, x1:x2), #<<
    c(x1 = -1.5080, x2 = 1.5418), #<<
    tolerance = 1e-3,
    ignore_attr = TRUE
  )
})
```

@@

```{r recipe, fig.alt='https://www.10000recipe.com/recipe/6839413', out.width='100%'}
knitr::include_graphics("images/bibimbap-recipe-10000recipe.png")
```

@@

>>>>

`df1 <- tibble()` \# 데이터 생성
{{content}}

@@

`f1 <- function() {}` \# **함수 정의**
{{content}}

@@

`f2 <- function() {}` \# **함수 정의**
{{content}}

@@

`df1 %>% f1() %>% f2()` \# 분석
{{content}}

@@

`f3 <- function() {}` \# **함수 정의**
{{content}}

@@

`df1 %>% f1() %>% f3()` \# 분석
{{content}}

@@

`df2 <- tibble()` \# 데이터 생성
{{content}}

@@

`f4 <- function() {}` \# **함수 정의**
{{content}}

@@

`f5 <- function() {}` \# **함수 정의**
{{content}}

@@

`df2 %>% f1() %>% f4() %>% f5()` \# 분석
{{content}}

@@

````
```{r}`r ''`
*library(dmtr)

@@

```{r lda-test, echo = TRUE}
library(testthat); library(dmtr);
test_that("Fisher discriminant function matches", {
  local_edition(3)
  expect_equal( #<<
    fisher_ld(binaryclass2, class, x1:x2), #<<
    c(x1 = -1.5080, x2 = 1.5418), #<<
    tolerance = 1e-3,
    ignore_attr = TRUE
  )
})
```

@@

```{r recipe, fig.alt='https://www.10000recipe.com/recipe/6839413', out.width='100%', fig.cap='https://www.10000recipe.com/recipe/6839413'}
knitr::include_graphics("images/bibimbap-recipe-10000recipe.png")
```

@@

---
class: center, middle, inverse

# 감사합니다
